---
title: "data.table Homework"
author: "Carson Cherniss and Ainsley Gallagher"
date: "2025-03-04"
format: pdf
---
```{r loading-packages, message=FALSE, warning=FALSE}
library(tidyverse)
library(data.table)

```

```{r loading-data, message=FALSE, warning=FALSE}
flights1 <- fread("nycdata.csv")
flights2 <- read_csv("nycdata.csv")
```

## 1: Use and show data.table code to select the variables year, month, day, and hour from the imported flights data
```{r question 1}
flights1[, c("year", "month", "day", "hour")]
```

## 2: Use and show data.table code to produce a table that shows a carrier of DL, an origin of JFK and a destination of SEA
```{r question 2}
flights1[carrier == "DL" & origin == "JFK" & dest == "SEA", c("carrier","origin","dest")]
```

## 3: Use and show data.table code to produce a table that shows a carrier of UA, a month of March, and an airtime that is below 330.
```{r question 3}
flights1[carrier == "UA" & month == 3 & air_time < 330, c("carrier", "month", "air_time")]
```

## 4: Use and show tidyverse code to produce a table that shows a carrier of UA, a month of March, and an airtime that is below 330.
```{r question 4}
flights2 |>  
  select(carrier, month, air_time) |> 
  filter(carrier == "UA", month == 3, air_time < 330) 
```

## 5: Use the data.table method to add a variable called speed that is the average air speed of the plane in miles per hour.
```{r question 5}
# R code  here

```

## 6: Use the tidyverse method to add a variable called speed that is the average air speed of the plane in miles per hour.
```{r question 6}
# R code  here

```

## 7: Show and use coding to change the carrier abbreviation of UA to UniitedAir,
### 7a: data.table method
```{r question 7a}
# R code  here

```

### 7b: tidyverse method (Use a sequence of dplyr commands so that you can see the change in your table)
```{r question 7b}
# R code  here

```
